Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-05-24 analysis/preregistration_template.Rmd
Add Libby as a template author
Add @LibbyR as an author after incorporating her changes on the .md file.

---
title: "Ecology and Conservation Modelling Preregistration Template -- DRAFT"
author: "Elise Gould, Megan Good, TBD:workshop collaborators"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document: default
bibliography: ../data/references.bib
---

>>>>

---
title: "Ecology and Conservation Modelling Preregistration Template -- DRAFT"
author: "Elise Gould, Megan Good, Libby Rumpff, TBD:workshop collaborators"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  github_document: default
bibliography: ../data/references.bib
---
